### 2016-07-06 text/building_path_conditions.tex
Updates to building PCs.

As well, we present our approach to building a set of path conditions to represent all executions of a DSLTrans transformation.

@@

 This section will describe how path conditions are constructed for a DSLTrans transformation using our approach.

@@

A new set of path conditions will then be created by sequentially combining each rule in the layer with the path condition selected. Recall that a path condition represents a set of rules that have symbolically executed, thereby abstracting a set of transformation executions through our abstraction relation. \reviewer{we cannot recall this as it has not yet been presented;
the abstraction relation is defined only in Section 5}Combining a path condition with a rule will produce one or more path conditions depending on how the rule combines with the rules already represented by the path condition. The pre- and post- conditions defined by the path condition will be modified according to the elements found in that rule.

>>>>

In this section we present our approach to building a set of path conditions to represent all executions of a DSLTrans transformation.

@@

@@

A new set of path conditions will then be created by sequentially combining each rule in the layer with the path condition selected. Recall from \cref{subsec:gen_path_conds} that a path condition represents a set of rules that have symbolically executed, thereby abstracting a set of transformation executions through our abstraction relation. Combining a path condition with a rule will produce one or more path conditions depending on how the rule combines with the rules already represented by the path condition. The pre- and post- conditions defined by the path condition will be modified according to the elements found in that rule.
